---
title: "Aides Tests"
author: "Vanessa Michel"
date: "December 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Introduction

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?

We are going to address two research questions in our analysis of the 3 drugs tested during these clinical trials. We want to answer the following:
Are the drugs effective in preventing Aids? Are the drugs sex specific?


#Methods

We will be using a combination of graphical and numerical tests to analyze the data, including barcharts and two-way tables. We will also use a chi-squared test to measure our inferential results. For each test we will look at whether or not the drug that got administered was effective in preventing Aids for each of the sample pouplations. We will then take a look further into the results to obvserve whether or not each drug administered was sex specific. 

#Results  

## Descriptive Results  

### Graphical Descriptive Results  

##### **South Carolina Aids Bar Chart:**  

```{r}
barchartGC(~infected + group, data=Scarolina, type="percent")
```

After viewing the data graphically, it appears that there was a slightly higher percentage of people in the **Aids** group that received the placebo than received the drug. In the **Non-Aids** group, it appears that the same amount of people received the drug that received the placebo. The drug does not appear to have had a signigicant effect on prevention of Aids in the South Carolina Group. 


 We will subset the data by sex to see if the drug is sex specific.
 

##### **South Carolina Aids Bar Chart (Males):**  
```{r}
ScarolinaM <- filter(Scarolina,sex=="M")
barchartGC(~infected + group, data=ScarolinaM, type="percent")
```

After viewing the data graphically, it appears that there is a higher percentage of men in the **Aids** group who received the drug than there were who received the placebo. In the **non-Aids** group, there was a slightly lower percentage of males who received the drug than received the placebo. The drug seems to be ineffective in preventing Aids in the Men in South Carolina. It appears that the drug may be giving these Men Aids.



##### **South Carolina Aids Bar Chart (Females):**   
```{r}
ScarolinaF <- filter(Scarolina,sex=="F")
barchartGC(~infected + group, data=ScarolinaF, type="percent")
```

After viewing the data graphically, it appears that of the women in the **non-Aids** group a slightly larger percentage received the drug. Of the women in the **Aids** group, a much lower percentage received the drug than received the placebo. This drug appears to be effective in preventing Aids in females in South Carolina. This drug appears to be sex specific. While causing a higher percentage of Males to get Aids, it seems to have the opposite effect on Women in South Carolina. 



##### **Central Africa Aids Bar Chart:**   
```{r}
barchartGC(~infected + group, data=cenAfrica, type="percent")
```

After viewing the data graphically, it appears that in the **non-Aids** group, an equal amount of people received the drug vs. the placebo. Of the people in the **Aids** group, a slightly lower percentage of participants received the drug vs. the placebo. The drug appears to have slightly lowered the number of people with Aids in Central Africa, though it does not seem to be very significant. 


We will subset the data by sex to see if the drug is sex specific.  


##### **Central Africa Aids Bar Chart (Males):**  
```{r}
cenAfricaM <- filter(cenAfrica,sex=="M")
barchartGC(~infected + group, data=cenAfricaM, type="percent")
```

After viewing the data graphically, it appears that the two groups are very similar. In both the **aids** and **non-Aids** groups, there is about the same percentage of people who received the drug vs. the placebo. Although in the **aids** group, the percentage of people who received the drug was slightly lower than the number who received the placebo. The drug does not appear to have been effective in preventing Aids in Males in Central Africa.



##### **Central Africa Aids Bar Chart (Females):**   
```{r}
cenAfricaF <- filter(cenAfrica,sex=="F")
barchartGC(~infected + group, data=cenAfricaF, type="percent")
```

After viewing the data graphically, it appears that there is a lower percentage of Females in the **Aids** group who received the drug than received the placebo. In the **non-Aids** group, about the same percentage of Females received the drug vs. the placebo. The drug appears to have had a positive effect in preventing Aids in Females in Central Africa. The drug appears to be sex specifc, while having no effect on Males, it was effective in Females. 



##### **Korea Aids Bar Chart:**   
```{r}
barchartGC(~infected + group, data=korea, type="percent")
```

After viewing the data graphically, it appears that there is a smaller percentage of participants in the **Aids** group who received the drug than received the placebo. Of the **non-Aids** group the results were about the same whether a person received the drug or the placebo. It appears the drug was effective in preventing Aids in Korea. 


We will subset the data by sex to see if the drug is sex specific. 


##### **Korea Aids Bar Chart (Males):**  
```{r}
koreaM <- filter(korea,sex=="M")
barchartGC(~infected + group, data=koreaM, type="percent")
```

After viewing the data graphically, it appears that there is a much lower percentage of Males in the **aids** group who received the drug vs. the placebo. In the **non-Aids** group, there was a slightly higher percentage of people who received the drug. This drug appears to be effective in preventing Aids in Males in Korea. 



##### **Korea Aids Bar Chart (Females):**   
```{r}
koreaF <- filter(korea,sex=="F")
barchartGC(~infected + group, data=koreaF, type="percent")
```

After viewing the data graphically, it appears that the **aids** group has a much higher percentage of Females who received the drug than the placebo. In the **non-Aids** group, about the same amount of people received the drug vs. the placebo. The drug does not appear to be effective in preventing Aids in Females in Korea. It appears this drug is causing Aids in Females in Korea.This drug appears to be sex specific. While it was effective in preventing Aids in Males in Korea, it seems to have had the opposite effect in the Women. 


#Numerical Descriptive Results

To view the results of our data numerically, we will use a two-way table with row percents.


##### **South Carolina Two-way Table:**  

```{r}
Scarolina_table <- xtabs(~infected + group, data=Scarolina)
rowPerc(Scarolina_table)
```

Of those in the **Aids** group, 49.37% recevied the drug, 50.53% received the placebo.   
Of those in the **non-Aids** group, 50.04% received the drug, 49.96% received the placebo.   
After viewing the data numerically, it appears that this drug did not have any significant affect on the prevention of Aids in the clinical trial in South Carolina.   


We will separate the data by sex, creating a separate two way table for each sex to see if drug is sex specific.         

##### **South Carolina Two-way Table (Males):**  

```{r}
ScarolinaM_table <- xtabs(~infected + group, data=ScarolinaM)
rowPerc(ScarolinaM_table)
```

Of those Males in the **Aids** group, 57.35% received the drug, 42.65% received the placebo.  
Of those Males in the **non-Aids** group, 49.52% received the drug, 50.48% received the placebo.   
After viewing the data numerically, it appears that this drug was not effective in preventing Aids in Males in South Carolina. It seems that the drug is giving the Males Aids.    


##### **South Carolina Two-way Table (Females):**  
```{r}
ScarolinaF_table <- xtabs(~infected + group, data=ScarolinaF)
rowPerc(ScarolinaF_table)
```

Of those Females in the **Aids** group, 38.83% received the drug, 61.17% received the placebo.   
Of those Females in the **non-Aids** group, 50.55% received the drug, 49.45% received the placebo.    
After viewing the data numerically, it appears that this drug was effective in preventing Aids in Females in South Carolina. This is opposite from the results this drug had on Males. This drug appears to be sex specific. 

##### **Central Africa Two-way Table:**  

```{r}
cenAfrica_table <- xtabs(~infected + group, data=cenAfrica)
rowPerc(cenAfrica_table)
```

Of those in the **Aids** group, 47.87% received the drug,52.13% received the placebo.    
Of those in the **non-Aids** group, 50.10% received the drug, 49.90% received the placebo.     
After viewing the data numerically, it appears that this drug had a very small effect on preventing Aids in the people in Central Africa.

We will separate the data by sex, creating a separate two way table for each sex to see if drug is sex specific.     

##### **Central Africa Two-way Table (Males):** 

```{r}
cenAfricaM_table <- xtabs(~infected + group, data=cenAfricaM)
rowPerc(cenAfricaM_table)
```

Of those Males in the **Aids** group, 49.47% received the drug, 50.53% received the placebo.    
Of those Males in the **non-Aids** group, 50.02% received the drug, 49.98% received the placebo.    
After viewing the data numerically, it appears that this drug did not have any significant effect on preventing Aids in Males in Central Africa. 



##### **Central Africa Two-way Table (Females):**  

```{r}
cenAfricaF_table <- xtabs(~infected + group, data=cenAfricaF)
rowPerc(cenAfricaF_table)
```

Of those Females in the **Aids** group, 46.55% received the drug, 53.45% received the placebo.   
Of those Females in the **non-Aids** group, 50.17% received the drug, 49.83% received the placebo.    
After viewing the data numerically, it appears that this drug was effective in preventing Aids in Women in Central Africa. 



##### **Korea Two-way Table:**  

```{r}
korea_table <- xtabs(~infected + group, data=korea)
rowPerc(korea_table)
```

Of those in the **Aids** group, 44.02% received the drug, 55.98% received the placebo.    
Of those in the **non-Aids** group, 50.33% received the drug, 49.67% received the placebo.    
After viewing the data numerically, it appears that this drug was effective in preventing Aids in Korea. 


We will separate the data by sex, creating a separate two way table for each sex to see if drug is sex specific.    

##### **Korea Two-way Table (Males):**  

```{r}
koreaM_table <- xtabs(~infected + group, data=koreaM)
rowPerc(koreaM_table)
```

Of those Males in the **Aids** group, 32.68% received the drug, 67.32% received the placebo.   
Of those Males in the **non-Aids** group, 51.25% received the drug, 48.75% received the placebo.   
After viewing the data numerically, it appears that this drug was effective in preventing Aids in the Males in Korea. 



##### **Korea Two-way Table (Females):** 

```{r}
koreaF_table <- xtabs(~infected + group, data=koreaF)
rowPerc(koreaF_table)
```

Of those Females in the **Aids** group, 65.43% received the drug, 34.57% received the placebo.   
Of those Females in the **non-Aids** group, 49.43% received the drug, 50.57% received the placebo.   
After viewing the data numerically, it appears that this drug was not effective in preventing Aids in Females. It appears that the drug is leading to Aids in Females, which is the opposite effect as it had on the Males. The drug appears to be sex specific. 



#Inferential Results
Looking at the graphical and numerical results alone is not enough to tell us whether our results will also apply to the population at large. To do so, we will need to run an inferential test. The one we will use is a chi-square test.   

We will now run 9 chi-square tests. We will run these tests with the following assumptions:

* There is no relationship between the drug and prevention of Aids.
* There is no relationship between sex and the efficacy of the drug in preventing Aids. 

##### **South Carolina chi-square test:**     
Let us begin by forming our two hypotheses:   
* $H_0$: There is no relationship between the drug and prevention of Aids.  
* $H_a$: There is a relationship between the drug and prevention of Aids.

```{r}
chisqtestGC(Scarolina_table)
```
Our P-value is 0.8942. This means that the probability of getting a sample like this under conditions where the null hypothesis is true is about 89%. This is well above our threshold of 5%. Therefore, we will accept the null hypothesis and conclude that there is no relationship between this drug and prevention of Aids.     
    

##### **South Carolina chi-square test (Males):**      
We will form our two hypothesis:    
* $H_0$: There is no relationship between the drug and preventing Aids in Males.  
* $H_a$: There is a relationship between the drug and preventing Aids in Males. 

```{r}
chisqtestGC(ScarolinaM_table)
```

Our P-value is 0.0926. Our chances of getting such a result are higher than our threshold of 5%. Therefore, we accept the null hypothesis and conclude that there is no relationship between this drug and prevention of Aids in Males.    

##### **South Carolina chi-square test (Females):**   
We will form our two hypothesis:    
* $H_0$: There is no relationship between the drug and preventing Aids in Females.  
* $H_a$: There is a relationship between the drug and preventing Aids in Females.   

```{r}
chisqtestGC(ScarolinaF_table)
```

Our P-value is 0.0264. The probability of getting a sample like this under these conditions is about 2 out of 100. This is below our threshold of 5%. Since the p-value is too low, we will reject the null hypothesis and conclude that there is a relationship between this drug and prevention of Aids in Females.   

##### **Central Africa chi-square test:**     
Let us form our two hypotheses:   
* $H_0$: There is no relationship between the drug and prevention of Aids.  
* $H_a$: There is a relationship between the drug and prevention of Aids.  

```{r}
chisqtestGC(cenAfrica_table)
```
Our P-value is 0.5735. The chances of getting a sample like this are high (about 57%), which is well above our threshold of 5%. Therefore, we will accept the null hypothesis and conclude that there is no relationship between this drug and prevention of Aids. 

##### **Central Africa chi-square test (Males):**   
We will form our two hypothesis:    
* $H_0$: There is no relationship between the drug and preventing Aids in Males.  
* $H_a$: There is a relationship between the drug and preventing Aids in Males. 

```{r}
chisqtestGC(cenAfricaM_table)
```
Our P-value is 1. The chances of getting results like this are extremely high. We will accept the null hypothesis and conclude that there is no relationship between this drug and preventing Aids in Males.   

##### **Central Africa chi-square test (Females):**   
We will form our two hypothesis:    
* $H_0$: There is no relationship between the drug and preventing Aids in Females.  
* $H_a$: There is a relationship between the drug and preventing Aids in Females. 

```{r}
chisqtestGC(cenAfricaF_table)
```
Our P-value is 0.5055, about 50%. Since our p-value is so high, we will accpet the null hypothesis and conclude that there is no relationship between this drug and preventing Aids in Females.

##### **Korea chi-square test:**   
Let us form our two hypotheses:   
* $H_0$: There is no relationship between the drug and prevention of Aids.  
* $H_a$: There is a relationship between the drug and prevention of Aids.  

```{r}
chisqtestGC(korea_table)
```
Our p-value is 0.0699, which is above our threshold of 5%. Therefore, we will accept the null hypothesis and conclude that there is no relationship between this drug and preventing Aids in Korea.

##### **Korea chi-square test (Males):**   
We will form our two hypothesis:    
* $H_0$: There is no relationship between the drug and preventing Aids in Males.  
* $H_a$: There is a relationship between the drug and preventing Aids in Males. 

```{r}
chisqtestGC(koreaM_table)
```
Our P-value is 0. The chances of getting such a result are extremely small. Therefore, we will choose to reject the null hypothesis. So it appears that there is a relationship between this drug and preventing Aids in Males. 

##### **Korea chi-square test (Females):**   
We will form our two hypothesis:    
* $H_0$: There is no relationship between the drug and preventing Aids in Females.  
* $H_a$: There is a relationship between the drug and preventing Aids in Females. 

```{r}
chisqtestGC(koreaF_table)
```
Our p-value is 0.0066. The chances of getting such a result are extremely low. Therefore, we will reject the null hypothesis. It appears that there is a relationship between this drug and preventing Aids in Females.   

#Discussion and Conclusion  
After viewing the results graphically, numerically, and running chi-square tests on the data, we can conclude the following: