---
title: "Aides Tests"
author: "Vanessa Michel"
date: "November 29, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Introduction

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?

Our research question is:
Is taking the drug effective in preventing Aids in Females?
Is taking the drug effective in preventing Aids in Males?

#Methods

We will be using the graphical and numerical tests: barcharts and two-way tables. We will be using a chi-squared test to measure our inferential results.

#Results

# Descriptive Results

## Graphical Descriptive Results

# South Carolina  
 We will subset the data by sex to see if the drug is sex specific.

### South Carolina Aids Results (Males)  
```{r}
ScarolinaM <- filter(Scarolina,sex=="M")
barchartGC(~infected + group, data=ScarolinaM, type="percent")
```

After viewing the data graphically, it appears that there are more men in the **Aids** group who received the drug than there were in the **non-Aids** group who received the drug. The drug seems to be ineffective in Men in South Carolina and may be increasing Aids in this population. 

### South Carolina Aids Results (Females)  
```{r}
ScarolinaF <- filter(Scarolina,sex=="F")
barchartGC(~infected + group, data=ScarolinaF, type="percent")
```

After viewing the data graphically, it appears that there are more women in the **non-Aids** group who received the drug than there were in the **Aids** group. The drug appears to be effective in Women of South Carolina.  


# Central Africa  

We will subset the data by sex to see if the drug is sex specific.  

### Central Africa Aids Results (Males)  
```{r}
cenAfricaM <- filter(cenAfrica,sex=="M")
barchartGC(~infected + group, data=cenAfricaM, type="percent")
```

### Central Africa Aids Results (Females)  
```{r}
cenAfricaF <- filter(cenAfrica,sex=="F")
barchartGC(~infected + group, data=cenAfricaF, type="percent")
```

# Korea  

We will subset the data by sex to see if the drug is sex specific. 

### Korea Aids Results (Males)  
```{r}
koreaM <- filter(korea,sex=="M")
barchartGC(~infected + group, data=koreaM, type="percent")
```

### Korea Aids Results (Females)  
```{r}
koreaF <- filter(korea,sex=="F")
barchartGC(~infected + group, data=koreaF, type="percent")
```

#Numerical Descriptive Results

To view the results of our data numerically, we will use a two-way table with row percents.

#Inferential Results
Looking at the graphical and numerical results alone is not enough to tell us whether our results will also apply to the population at large. To do this, we will run a chi-square test.


#Discussion and Conclusion  
After viewing the results graphically, numerically, and running chi-square tests on the data, we can conclude the following: