---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Introduction

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?

Our research question is:
Is taking the drug effective in preventing Aids in Females?
Is taking the drug effective in preventing Aids in Males?

#Methods

We will be using the folloiwng methods: bar charts, two-way tables and a chi-squared test.

#Results

# Descriptive Results

## Graphical Descriptive Results

# South Carolina

We will subset the data by sex to see if the drug is sex specific.
### South Carolina Aids Results (Males)
```{r}
ScarolinaM <- filter(Scarolina,sex=="M")
barchartGC(~infected + group, data=ScarolinaM, type="percent")
```

### South Carolina Aids Results (Females)
```{r}
ScarolinaF <- filter(Scarolina,sex=="F")
barchartGC(~infected + group, data=ScarolinaF, type="percent")
```
The amount of females infected is lower when receiving the drug. However, the amount of males affected is higher when receiving the drug. 


# Central Africa

We will subset the data by sex to see if the drug is sex specific.
### Central Africa Aids Results (Males)
```{r}
cenAfricaM <- filter(cenAfrica,sex=="M")
barchartGC(~infected + group, data=cenAfricaM, type="percent")
```

### Central Africa Aids Results (Females)
```{r}
cenAfricaF <- filter(cenAfrica,sex=="F")
barchartGC(~infected + group, data=cenAfricaF, type="percent")
```

# Korea

We will subset the data by sex to see if the drug is sex specific.
### Korea Aids Results (Males)
```{r}
koreaM <- filter(korea,sex=="M")
barchartGC(~infected + group, data=koreaM, type="percent")
```

### Korea Aids Results (Females)
```{r}
koreaF <- filter(korea,sex=="F")
barchartGC(~infected + group, data=koreaF, type="percent")
```